Generating Images From Captions\\ With Attention

### 2015-11-05 supp.tex
a

Each parameter in alignDRAW was initialized by sampling from a Gaussian distribution with 
mean $0$ and standard deviation $0.01$. The model was trained using \textit{RMSprop} with an initial learning rate of $0.001$. The norm of the gradients was clipped at a maximum of $10.0$ during training to deal with exploding gradients. We used a vocabulary size of $K = 25323$ and $K = 22$ for Microsoft COCO and MNIST with Captions respectively. All capital letters in the words were converted to small letters as a preprocessing step. For all tasks, $\overrightarrow{h}^{lang}_{n}$ and $\overleftarrow{h}^{lang}_{n}$ in the language model had $128$ units. The parameters in the \textit{align} operator had a dimensionality of $l = 512$, $\vv \in \mathbb{R}^{512}$, $U \in \mathbb{R}^{512 \times 256}$, $W \in \mathbb{R}^{512 \times n^{gen}}$ and $b \in \mathbb{R}^{512}$. For the Microsoft COCO task, the alignDRAW model was trained for $18$ epochs and the learning rate was reduced by the factor of $0.1$ after $11$ epochs. The architectural configurations of alignDRAW models are shown on Table~\ref{tab:drawhyper}.

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c | c c c c c c}
\hline
\multicolumn{7}{c}{\textbf{alignDRAW Model}} \\
\hline
Task & \#glimpses & Inference \#$h$ & Generative \#$h$ & \#$z$ & Read Size & Write Size\\
\hline
Microsoft COCO & 32 & 550 & 550 & 275 & 9 & 9\\
MNIST Captions & 32 & 300 & 300 & 150 & 8 & 8\\
\end{tabulary}
\caption{The architectural configurations of alignDRAW models.}
\label{tab:drawhyper}
\end{center}
%\vspace{-0.3cm}
\end{table}

@@

\subsection*{Evaluation}

Table~\ref{tab:nll} shows the estimated variational lower bound on the average train/validation/test 
log-probabilities.
Note that the alignDRAW model does not suffer much from overfitting. 
The results worsened dramatically after sharpening test images.

@@

\newpage
\section*{Appendix C: Effect of Sharpening Images.}
\label{sec:post_processing}

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-stop-sign-is-flying-in-blue-skies-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-flying-in-the-blue-skies-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-toilet-seat-sits-open-in-the-grass-field-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-person-skiing-on-sand-clad-vast-desert-blurry.png}}\\

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-stop-sign-is-flying-in-blue-skies-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-flying-in-the-blue-skies-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-toilet-seat-sits-open-in-the-grass-field-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-person-skiing-on-sand-clad-vast-desert-sharp.png}}\\

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-blurry.png}}\\

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\\

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/the-decadent-chocolate-dessert-is-on-the-table-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-bowl-of-bananas-is-on-the-table-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-cat-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-dog-blurry.png}}\\

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/the-decadent-chocolate-dessert-is-on-the-table-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-bowl-of-bananas-is-on-the-table-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-cat-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-vintage-photo-of-a-dog-sharp.png}}\\

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-blue-skies-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-rainy-skies-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-dry-grass-field-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-green-grass-field-blurry.png}}\\

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-blue-skies-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-rainy-skies-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-dry-grass-field-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-green-grass-field-sharp.png}}\\

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-desert-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-forest-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-beach-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-sun-blurry.png}}\\

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-desert-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-forest-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-beach-sharp.png}}\quad

@@

]{\includegraphics[width=0.23\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-sun-sharp.png}}\\

@@

\caption{\small Effect of sharpening images previously shown in the publication.}

>>>>

Each parameter in alignDRAW was initialized by sampling from a Gaussian distribution with 
mean $0$ and standard deviation $0.01$. 
The model was trained using \textit{RMSprop} with an initial learning rate of $0.001$. 
For the Microsoft COCO task, we trained our model for $18$ epochs. The learning rate was 
reduced to $0.0001$ after $11$ epochs.
\FIXME{For the MNIST with Captions task, the model was trained for ??? epochs and the 
learnign rate was reduced to ?? after ?? epochs}.   
The norm of the gradients was clipped at $10$ during training 
to avoid the exploding gradients problem.

We used a vocabulary size 
of $K = 25323$ and $K = 22$ for the Microsoft COCO and MNIST with Captions datasets respectively. 
All capital letters in the words were converted to small letters as a preprocessing step. 
For all tasks, the hidden states $\overrightarrow{h}^{lang}_{i}$ and $\overleftarrow{h}^{lang}_{i}$ 
in the language model had $128$ units. Hence the dimensionality of the 
concatenated state of the Bidirectional LSTM
$\hlang_{i} = [\overrightarrow{h}^{lang}_{i}, \overleftarrow{h}^{lang}_{i}]$ was~256. 
The parameters in the \textit{align} operator (\Eqref{eq:align2}) 
had a dimensionality of $l = 512$, so that 
$\vv \in \mathbb{R}^{512}$, $U \in \mathbb{R}^{512 \times 256}$, $W \in \mathbb{R}^{512 \times n^{gen}}$ and $b \in \mathbb{R}^{512}$. 
The architectural configurations of the alignDRAW models are shown in Table~\ref{tab:drawhyper}.

\begin{table}[!t]
\begin{center}
\begin{tabulary}{\linewidth}{c | c c c c c c}
\hline
\hline
 & & \multicolumn{3}{c}{\textbf{alignDRAW Model}}  & &  \\
\hline
Task & \#glimpses & Inference  & Generative  & Latent & Read Size & Write Size\\
     & \ T & Dim of $h^{infer}$ & Dim of $h^{gen}$  & Dim of $Z$  & $p$ & $p$\\
\hline
MS COCO & 32 & 550 & 550 & 275 & 9 & 9\\
MNIST   & 32 & 300 & 300 & 150 & 8 & 8\\
\end{tabulary}
\caption{The architectural configurations of alignDRAW models.}
\label{tab:drawhyper}
\end{center}
%\vspace{-0.3cm}
\end{table}

@@

\subsection*{Evaluation}
Table~\ref{tab:nll} shows the estimated variational lower bounds on the average train/validation/test 
log-probabilities.
Note that the alignDRAW model does not suffer much from overfitting. 
The results substantially worsen after sharpening test images.

@@

\newpage
\section*{Appendix C: Effect of Sharpening Images.}
\label{sec:post_processing}
\vspace{-0.1in}
Some examples of generated images before (top row) and after (bottom row) sharpening images 
using an adversarial network trained on residuals of a Laplacian 
pyramid conditioned on the skipthought vectors of the captions.

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-stop-sign-is-flying-in-blue-skies-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-herd-of-elephants-flying-in-the-blue-skies-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-toilet-seat-sits-open-in-the-grass-field-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-person-skiing-on-sand-clad-vast-desert-blurry.png}}\\

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-stop-sign-is-flying-in-blue-skies-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-herd-of-elephants-flying-in-the-blue-skies-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-toilet-seat-sits-open-in-the-grass-field-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-person-skiing-on-sand-clad-vast-desert-sharp.png}}\\

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-blurry.png}}\\

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-yellow-school-bus-parked-in-a-parking-lot-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-red-school-bus-parked-in-a-parking-lot-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-green-school-bus-parked-in-a-parking-lot-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-blue-school-bus-parked-in-a-parking-lot-sharp.png}}\\

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/the-decadent-chocolate-dessert-is-on-the-table-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-bowl-of-bananas-is-on-the-table-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-vintage-photo-of-a-cat-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-vintage-photo-of-a-dog-blurry.png}}\\

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/the-decadent-chocolate-dessert-is-on-the-table-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-bowl-of-bananas-is-on-the-table-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-vintage-photo-of-a-cat-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-vintage-photo-of-a-dog-sharp.png}}\\

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-blue-skies-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-rainy-skies-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-dry-grass-field-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-green-grass-field-blurry.png}}\\

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-blue-skies-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-very-large-commercial-plane-flying-in-rainy-skies-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-dry-grass-field-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-herd-of-elephants-walking-across-a-green-grass-field-sharp.png}}\\

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-desert-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-forest-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-beach-blurry.png}}\quad

@@

\subfloat[]{\includegraphics[width=0.21\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-sun-blurry.png}}\\

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-desert-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-rider-on-a-blue-motorcycle-in-the-forest-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-beach-sharp.png}}\quad

@@

]{\includegraphics[width=0.21\textwidth]{figures/new/a-surfer-,-a-woman-,-and-a-child-walk-on-the-sun-sharp.png}}\\

@@

\caption{\small Effect of sharpening images.}
